---
title: "Intriduction"
author: "Chistine"
date: ""
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = T,comment ="#>" )
library(binomial)

```

##The intoduction of binomial Package
The binomial package help you figure out the all the statistic features of binomial distributions, from the average value to the kurtosis. 
It also contains methods helps you summarize those values and visualize the results

 
###Create the distribution
The first thing you should do is to create the distribution(i.e the total trials, how many times of success and the success possibility)

You must keep in mind the trails must be a non-negative integer,succes shoulb be a non-negative integer no greater than trials and the possibility should be a value between 0 and 1

```{r}
trials1 <- 10L
prob1<- 0.3
success1 <- 5L
```
###bin_choose

The bin_choose function can help you calculate how many combinations happens when k times success in total n trials
The function takes 2 parameters: *k* is the number of success you want to test. *n* is the total number of trials,which can be a vector of integer less than trials

```{r}
bin_choose(n = 5, k = 2)
bin_choose(trials1, prob1)
bin_choose(5, 1:3)
```
###culculate the probability of binomial distribution
The bin_proibability function can help you calculate the probability happens when k times success in total n trials
* The function takes 3 parameters:
  - *success* is the number of success,which can be a vector of integer less than trials
  - *trials* is the total number of trials  
  - *prob* is the probability of success 
  
```{r}
library(FRACTION)
bin_probability(success1,trials1,prob1)
```

###See the distribution of probability 
This function bin_distribution help you see the distribution of probability of successs in binomial distribution
it takes 2 parameters: trials and prob, then will return a data.frame of all the distributions
```{r}
bin_distribution(trials1,prob1)
```

Then you can choose to plot the distribution by plot.bindis()

But first, you have to store the result of bin_distribution into a value of class "bindis"
```{r}
dis1 <- bin_distribution(trials1,prob1)
```
Then you can use the method plot to get a barplot
```{r}
plot(dis1)
```

###The cumulativeprobability
This function help you see the cumulative probability of binomial distribution.(i.e the probability of successing less than k time out of all the trials)
it takes 2 parameters: trials and prob, then will return a data.frame of all the cumulative distributions
```{r}
bin_cumulative(trials1,prob1)
```
Then you can also use the method plot to get a plot
But fisrtly, you have to store the result into a variance of class"bincum"
```{r}
dis2 <- bin_cumulative(trials1,prob1)
```
Then you can use the method plot.bincum to get a plot
```{r}
plot(dis2)
```

###Check the features
use the function bin_var to check your parameters and store them into a variable of class "binvar"
it also take 2 parameters:trials and prob
```{r}
binvar1 <- bin_variable(trials1,prob1)
binvar1
```
####Check the features
Then you get a variable of class "binvar"
You can use the method summary.binvar to access to the features of this binomial distribution
It will show the mean,variance,mode,skewness,kurtosis of this distribution
```{r}
summary(binvar1)
```

####Check the feature separately
You can also choose to check those features separately

* There are 5 features you can choose to test
  - mean:using the function bin_mean to get the average of binomial distribution
  - variance:using the function bin_variance to get the variance of binomial distribution
  - mode:using the function bin_mode to get the mode of binomial distribution
  - skewness:using the function bin_skewness to get the skewness of binomial distribution
  - kurtosis：using the function bin_kurtosis to get the kurtosis of binomial distribution

each of those functions takes 2 parameters: trials and prob,which means the total trials and success possibility
*examples*
```{r}
bin_mean(trials1,prob1)
bin_variance(trials1,prob1)
bin_mode(trials1,prob1)
bin_skewness(trials1,prob1)
bin_kurtosis(trials1,prob1)
```


